Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-05-18 msc-publication.tex
Merge back into one table, rotate to make data fit

\begin{table*}[t]
	\caption{Minimum and maximum tracer magnitudes and \(\ell^2\) error norms at \(t = \SI{10000}{\second}\) in the horizontal tracer advection tests using centred linear and cubic upwind-biased schemes, and the fourth order scheme from \citet{schaer2002}.}
\label{tab:advection}
%
\centering
\footnotesize
\begin{tabular}{ r @{\hspace{1.0em}} l @{\hspace{1.0em}} l @{\hspace{1.0em}} l l @{\hspace{1.0em}} l @{\hspace{1.0em}} l}
\hline\hline
& \multicolumn{3}{c}{Centred linear} & \multicolumn{3}{c}{Cubic upwind-biased} \\
& \(\ell^2\) error & min & max & \(\ell^2\) error & min & max \\
\hline
Analytic   & 0 & 0 & 1 & 0 & 0 & 1 \\
% 	     l2		     min	     max	   l2		    min		     max        
BTF 	   & \num{0.0210}  & \num{-0.275}  & \num{0.925} & \num{0.00791}  & \num{-0.0446}  & \num{0.925} \\
SLEVE      & \num{0.00233} & \num{-0.0252} & \num{0.985} & \num{0.00108}  & \num{-0.0106}  & \num{0.982} \\
Cut cell   & \num{0.00224} & \num{-0.0251} & \num{0.985} & \num{0.000577} & \num{-0.00674} & \num{0.983} \\
No terrain & \num{0.00223} & \num{-0.0251} & \num{0.985} & \num{0.000576} & \num{-0.00674} & \num{0.983} \\
\hline
\end{tabular}
\end{table*}

@@

\begin{table*}[t]
	\caption{Minimum and maximum tracer magnitudes and \(\ell^2\) error norms at \(t = \SI{10000}{\second}\) in the terrain following tracer advection test using centred linear and cubic upwind-biased schemes.}
\label{tab:advection}
%
\centering
\footnotesize
\begin{tabular}{ r @{\hspace{1.0em}} l @{\hspace{1.0em}} l @{\hspace{1.0em}} l l @{\hspace{1.0em}} l @{\hspace{1.0em}} l}
\hline\hline
& \multicolumn{3}{c}{Centred linear} & \multicolumn{3}{c}{Cubic upwind-biased} \\
& \(\ell^2\) error & min & max & \(\ell^2\) error & min & max \\
\hline
Analytic   & 0 & 0 & 1 & 0 & 0 & 1 \\
% 	     l2                        min                       max          l2                         min                       max
BTF 	   & \num{0.00251}           & \num{-0.0245}           & \num{0.985} & \num{0.00154}           & \num{-0.0110}           & \num{0.983} \\
SLEVE      & \num{0.0173}            & \num{-0.120}            & \num{0.950} & \num{0.0120}            & \num{-0.0263}           & \num{0.865} \\
Cut cell   & \num{13.6}              & \num{-623}              & \num{3480}  & \num{0.0134}            & \num{-0.028}            & \num{0.851} \\
\hline
\end{tabular}
\end{table*}

>>>>

@@

\begin{table*}[t]
	\caption{Minimum and maximum tracer magnitudes and \(\ell^2\) error norms at \(t = \SI{10000}{\second}\) in the horizontal and terrain following tracer advection tests using centred linear and cubic upwind-biased schemes and, for the horizontal advection test, the fourth order scheme from \citet{schaer2002}.}
\label{tab:advection}
%
\centering
\footnotesize
\begin{tabular}{l l l l S S S S}
\hline\hline
                  &                     &                  & Analytic & {BTF}   & {SLEVE}         & {Cut cell}     & {No terrain} \\
\hline
Horizontal        & Centred linear      & \(\ell^2\) error & 0        & 0.0210  & 0.00233         & 0.00224        & 0.00223     \\
                  &                     & min              & 0        & -0.275  & -0.0252         & -0.0251        & -0.0251     \\
                  &                     & max              & 1        & 0.925   & 0.985           & 0.985          & 0.985       \\
                  & Fourth order        & \(\ell^2\) error & 0        & 999     & 999             & {---}          & 999         \\
                  &                     & min              & 0        & 999     & 999             & {---}          & 999         \\
                  &                     & max              & 1        & 999     & 999             & {---}          & 999         \\
                  & Cubic upwind-biased & \(\ell^2\) error & 0        & 0.00791 & 0.00108         & 0.000577       & 0.000576    \\
                  &                     & min              & 0        & -0.0446 & -0.0106         & -0.000674      & -0.00674    \\
                  &                     & max              & 1        & 0.925   & 0.982           & 0.983          & 0.983       \\
\hline
Terrain following & Centred linear      & \(\ell^2\) error & 0        & 0.00251 & 0.0173          & 13.6           & {---}        \\
		  &                     & min              & 0        & -0.0245 & -0.120          & -623           & {---}        \\
                  &                     & max              & 1        & 0.985   & 0.950           & 3480           & {---}        \\
		  & Cubic upwind-biased & \(\ell^2\) error & 0        & 0.00154 & 0.0120          & 0.0134         & {---}        \\
                  &                     & min              & 0        & -0.0110 & -0.0263         & -0.028         & {---}        \\
                  &                     & max              & 1        & 0.983   & 0.865           & 0.851          & {---}        \\
\hline
\end{tabular}
\end{table*}
